---
title: "team"
author: "Nick Matthews; Jian"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Overall number of chocolate bars rated?
```{r}

choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
ratings <- choco$Rating

length(ratings)

```

### How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}
library(ggplot2)

years <- choco$Review.Date

barplot(table(choco$Review.Date))

```

We used table() function to get the number of times each year appeared in the data.
From the bar chart, it appears that the number of ratings on on chocolate increased from 2006-2008, then decreased in 2010. Then in continued to increase until 2013, and finally increased until 2015 before decreasing harshly from 2016-2017

### Which are the three locations with the most ratings? How do ratings compare across these company locations?
```{r}

top3location <- sort(table(choco$Company.Location), decreasing = TRUE)[1:3]
top3location

usaAvg = choco[choco$Company.Location=="U.S.A.",c(6,7)]
paste("USA average rating is ", mean(usaAvg$Rating))

franceAvg = choco[choco$Company.Location=="France",c(6,7)]
paste("France average rating is ", mean(franceAvg$Rating))

canadaAvg = choco[choco$Company.Location=="Canada",c(6,7)]
paste("Canada average rating is ", mean(canadaAvg$Rating))

```

I took the mean rating of all ratings for each location using the mean() function.

### Interesting question: Which company has the most ratings? What is its average rating by year?  
  
For our question, we found the company with the most ratings. This was Soma. First, I isolated all rows containing "Soma" in the company column. Then, I aggregated the data by year, averaging the rating for each of these years. See table below.  
This also brought up the question of comparison between multiple companies average rating per year. We did the same process for the top 3 most rated countries and used ggplot to put them *all on 1 graph*
```{r}

company_frequency <- sort(table(choco$Company), decreasing = TRUE)[1:3]
company_frequency_names <- names(company_frequency)
company_frequency_names

# Get the company with the most ratings
soma_ratings <- as.data.frame(choco[choco$Company=="Soma", ])

# Get the average rating per year for soma company
soma_rating_by_year <- aggregate(soma_ratings$Rating, by=list(soma_ratings$Review.Date),
                                FUN = mean)

# Rename the columns
names(soma_rating_by_year)[1] <- "Year"
names(soma_rating_by_year)[2] <- "Avg_Rating"

# A neat table showing the average ratings per year for Soma company
soma_rating_by_year

# Line plot for table
plot(x=soma_rating_by_year$Year, y=soma_rating_by_year$Avg_Rating, type = "l",
     xlab = "Year", ylab = "Average Rating", main = "Average rating per year for Soma")

```

```{r}

most3ratings <- choco[choco$Company %in% company_frequency_names,]

grouped <- aggregate(most3ratings$Rating, by=list(most3ratings$Company,
                      most3ratings$Review.Date),FUN = mean)
names(grouped)[1] <- "Company"
names(grouped)[2] <- "Year"
names(grouped)[3] <- "Average_Rating"

ggplot(grouped, mapping = aes(x=Year, y=Average_Rating, group=Company,
                              color=Company)) + geom_line()

```